---
title: "Tests for Picarro HT mode"
author: "Durban G Keeler"
date: "Sept 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

```{r}

# Input the directory containing the raw isotope data (subdirectory of 'Raw data')
HP.file.path = "Data/Raw Data/Calibrations/calibration_2018Sept14/HP_test/HIDS2272_IsoWater_20180915_204841.csv"
HT1.file.path = "Data/Raw Data/Calibrations/calibration_2018Sept14/HT_test/HIDS2272_HT_IsoWater_20180914_214604.csv"
HT2.file.path = "Data/Raw Data/Calibrations/calibration_2018Sept14/HT_test/HIDS2272_HT_IsoWater_20180917_150055.csv"

# Input the .Rdata file that contains the tray template sample/standards locations
template.path = "Data/Tray templates/calibrate_20180914.xlsx"

# Source and run the isotope reduction functions on given input files
source('R-functions/iso.reduce.R')
data.HP = iso.reduce(HP.file.path, template.path)
data.HT1 = iso.reduce(HT1.file.path, template.path)
data.HT2 = iso.reduce(HT2.file.path, template.path)

```


```{r}

bias.HT1 = data.frame(d18O = (data.HT1$d18O.correct-data.HP$d18O.correct), d18O.method = data.HT1$d18O.method, dD = data.HT1$dD.correct-data.HP$dD.correct, dD.method = data.HT1$dD.method)

bias.HT2 = data.frame(d18O = (data.HT2$d18O.correct-data.HP$d18O.correct), d18O.method = data.HT2$d18O.method, dD = data.HT2$dD.correct-data.HP$dD.correct, dD.method = data.HT2$dD.method)

plot(bias.HT1$d18O, pch = 16, col = 'red')
points(bias.HT2$d18O, pch = 16, col = 'blue')

plot(bias.HT1$dD[-3], pch = 16, col = 'red')
points(bias.HT2$dD[-3], pch = 16, col = 'blue')

```

```{r}

RMSE.HT1_d18O = sqrt(mean(bias.HT1$d18O^2))
RMSE.HT1_dD = sqrt(mean(bias.HT1$dD[-3]^2))
RMSE.HT2_d18O = sqrt(mean(bias.HT2$d18O^2))
RMSE.HT2_dD = sqrt(mean(bias.HT2$dD[-3]^2))

```

For the first high-throughput test, the additional added error compared to the high-precision mode had a median of `r format(median(bias.HT1$d18O), digits = 3)` with a RMSE of `r format(RMSE.HT1_d18O, digits = 4)` for $\delta O^{18}$, and a median of `r format(median(bias.HT1$dD[-3]), digits = 3)` with a RMSE of `r format(RMSE.HT1_dD[-3], digits = 4)` for $\delta D$. 

For the second high-throughput test, the additional added error had a median of `r format(median(bias.HT2$d18O), digits = 3)` with a RMSE of `r format(RMSE.HT2_d18O, digits = 4)` for $\delta O^{18}$, and a median of `r format(median(bias.HT2$dD[-3]), digits = 3)` with a RMSE of `r format(RMSE.HT2_dD[-3], digits = 4)` for $\delta D$. 
